Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond

### 2024-02-11 outputs/paper/paper.qmd
Update the reference
Update paper.qmd

# Introduction
1) broader context to motivate
According to dictionary, birth rate is defined as " ."

2) some detail about what the paper is about
3) a clear gap that needs to be filled
4) what was done
5) what was found
6) why it is important - replacement level fertility
7) the structure of the paper - 1. trend in US Birth Rates 2. Trends in Birth Rates by Population Subgroup 2.1 Five-year age group 2.2 Race and ethinicity

@@

@@

## Limitation
As mentioned in the original paper, the population subgroup can be diverged as they mix over the time. It is hard to sort out the race completely once they start to mixing it up. Therefore, over the time, we don't know the population subgroup Hispanic, Black, White are purely Hispanic, Black, White throughout the period.

@@

>>>>

# Introduction
1) broader context to motivate
2) some detail about what the paper is about
3) a clear gap that needs to be filled
4) what was done
5) what was found
6) why it is important - replacement level fertility
7) the structure of the paper - 1. trend in US Birth Rates 2. Trends in Birth Rates by Population Subgroup 2.1 Five-year age group 2.2 Race and ethinicity

@@

According to the Centers for Disease Control and Prevention, birth rate is defined as "the number of live births per 1,000 population." It is calculated by dividing the number of live births in a population in a year by the midyear resident population. More specifically, for census years, rates are based on unrounded census counts of the resident population as of April 1. For the noncensus years 1981 - 1989, rates are based on the midyear resident population, rounded to thousands (National Center for Health Statistics 2023). In an economical aspect, birth rates are an important factor that decides the growth of a country. In recent years, low birth rate became a conversation topic both nation-wide and worldwide. Many countries are rising this issue of declining birth rates and posing alternative measures to compensate the population drop. For instance,

@@

## Limitation
Beginning in 1997, the birth rate for the maternal age group 45-49 includes data for mothers aged 45 and over in the numerator and is based on the population of women aged 45-49 in the denominator (National Center for Health Statistics 2023). However as the dataset is missing for the population of women aged 45-49 before 1997 and the paper counts the data from the period 1980 to 2020, the women population in the age group 45-49 is eliminated.

As mentioned in the original paper, the population subgroup can be diverged as they mix over the time. It is hard to sort out the race completely once they start to mixing it up. Therefore, over the time, we don't know the population subgroup Hispanic, Black, White are purely Hispanic, Black, White throughout the period.

@@

---
nocite: '@*'
---
